An Experimental Analysis of the Influence of the Precision of Parameters in an Artificial Neural Network

### 2025-11-18 paper/main.tex
weiter

\subsection{Related Work}

Prior research in this domain can be broadly divided into methods that use
quantization already during training and methods that quantize a pretrained
model later at deployment time.

>>>>

\subsection{Related Work}
Prior research in this domain can be broadly divided into methods that use
quantization already during training and methods that quantize a pretrained
model later at deployment time.
